### 2015-05-24 docs/report/initialization.tex
Added library overview section
updates report benchmarks links.
fixes initialization tex section.

\section{Initialization}

As explained in the Web Workers standard \cite{w3c-ww} \textit{``Generally, workers are expected to be long-lived, have a high start-up performance cost, and a high per-instance memory cost."}.

@@

\subsubsection{Cold start benchmark}
The following is the code for the benchmark:
\bmcode{http://jsperf.com/worker-cold-start/5}{../../spikes/2.1.1/newVsPreExistent.js}

@@

\subsection{High per-instance memory cost}
The second factor makes it important for users to be able to control/limit the amount of web workers that the library instantiates. For that reason the library allows users to specify a maximum amount of workers to be instantiated, and also provide through its API a way to terminate all workers in existance.

>>>>

\section{Initialization}\label{sec:initialization}

As explained in the Web Workers standard \cite{w3c-ww-startup} \textit{``Generally, workers are expected to be long-lived, have a high start-up performance cost, and a high per-instance memory cost."}.

@@

\subsubsection{Cold start benchmark}
The following is the code for the benchmark:
\bmcode{http://jsperf.com/worker-cold-start/6}{../../spikes/2.1.1/newVsPreExistent.js}

@@

\subsection{High per-instance memory cost}
The second factor makes it important for users to be able to control/limit the amount of web workers that the library instantiates. For that reason the library allows users to specify a maximum amount of workers to be instantiated, and also provide through its API a way to terminate all workers in existence.
